Bayesian Sparsification of $\cplx$-valued networks

### 2019-12-06 paper/paper.tex
abstract stub

>>>>

\begin{abstract}
With continual miniaturization ever more applications of deep learning can be found in
embedded systems. Common embedded applications include on-device image recognition and
signal processing (audio and radio). We investigate complex-domain deep neural networks
and complex-valued Bayesian compression thereof. To this end we conduct a large scale
numerical study of complex-valued networks to assess quality - compression rate trade-off.
The results of this study have direct implications for real-time signal processing
throughput of embedded systems.
\end{abstract}
